Formal Modeling and Verification of a Rate-Monotonic Scheduling Implementation with Real-Time Maude

### 2016-11-09 RMS/final-version/TXT_15-TIE-3480.tex
included bbl into TXT.tex

%\documentclass[onecolumn]{IEEEtranTIE}
\documentclass[journal]{IEEEtranTIE}
\usepackage{graphicx}
\usepackage[noadjust]{cite}
\usepackage{picinpar}
\usepackage{amsmath}
\usepackage{stfloats}
\usepackage{url}
\usepackage{flushend}
\usepackage[latin1]{inputenc}
\usepackage{colortbl}
\usepackage{soul}
\usepackage{multirow}
\usepackage{pifont}
\usepackage{color}
\usepackage{alltt}
\usepackage[hidelinks]{hyperref}
\usepackage{enumerate}
\usepackage{siunitx}
\usepackage{breakurl}
\usepackage{epstopdf}
\usepackage{pbox}

@@

\bibliographystyle{Bibliography/IEEEtranTIE}
\bibliography{Bibliography/IEEEabrv,Bibliography/BIB_15-TIE-3480}\

>>>>

%\documentclass[onecolumn]{IEEEtranTIE}
\documentclass[journal]{IEEEtranTIE}
\usepackage{graphicx}
\usepackage[noadjust]{cite}
\usepackage{picinpar}
\usepackage{amsmath}
\usepackage{stfloats}
\usepackage{url}
\usepackage{flushend}
\usepackage[latin1]{inputenc}
\usepackage{colortbl}
\usepackage{soul}
\usepackage{multirow}
\usepackage{pifont}
\usepackage{color}
\usepackage{alltt}
\usepackage[hidelinks,bookmarks=false]{hyperref}
\usepackage{enumerate}
\usepackage{siunitx}
\usepackage{breakurl}
\usepackage{epstopdf}
\usepackage{pbox}

@@

% Generated by IEEEtran.bst, version: 1.12 (2007/01/11)
\begin{thebibliography}{10}
\providecommand{\url}[1]{#1}
\csname url@samestyle\endcsname
\providecommand{\newblock}{\relax}
\providecommand{\bibinfo}[2]{#2}
\providecommand{\BIBentrySTDinterwordspacing}{\spaceskip=0pt\relax}
\providecommand{\BIBentryALTinterwordstretchfactor}{4}
\providecommand{\BIBentryALTinterwordspacing}{\spaceskip=\fontdimen2\font plus
\BIBentryALTinterwordstretchfactor\fontdimen3\font minus
  \fontdimen4\font\relax}
\providecommand{\BIBforeignlanguage}[2]{{%
\expandafter\ifx\csname l@#1\endcsname\relax
\typeout{** WARNING: IEEEtran.bst: No hyphenation pattern has been}%
\typeout{** loaded for the language `#1'. Using the pattern for}%
\typeout{** the default language instead.}%
\else
\language=\csname l@#1\endcsname
\fi
#2}}
\providecommand{\BIBdecl}{\relax}
\BIBdecl

\bibitem{DBLP:journals/jacm/LiuL73}
C.~L. Liu and J.~W. Layland, ``Scheduling algorithms for multiprogramming in a
  hard-real-time environment,'' \emph{J. {ACM}}, vol.~20,
  \href{http://dx.doi.org/10.1145/321738.321743}{DOI 10.1145/321738.321743},
  no.~1, pp. 46--61, 1973.

\bibitem{DBLP:conf/rtss/LehoczkySS87}
J.~P. Lehoczky, L.~Sha, and J.~K. Strosnider, ``Enhanced aperiodic
  responsiveness in hard real-time environments,'' in \emph{Proceedings of the
  8th {IEEE} Real-Time Systems Symposium {(RTSS} '87)}, 1987, pp. 261--270.

\bibitem{DBLP:journals/rts/SpruntSL89}
B.~Sprunt, L.~Sha, and J.~P. Lehoczky, ``Aperiodic task scheduling for hard
  real-time systems,'' \emph{Real-Time Systems}, vol.~1,
  \href{http://dx.doi.org/10.1007/BF02341920}{DOI 10.1007/BF02341920}, no.~1,
  pp. 27--60, 1989.

\bibitem{DBLP:conf/rtss/LehoczkyR92}
J.~P. Lehoczky and S.~Ramos{-}Thuel, ``An optimal algorithm for scheduling
  soft-aperiodic tasks in fixed-priority preemptive systems,'' in
  \emph{Proceedings of the Real-Time Systems Symposium},
  \href{http://dx.doi.org/10.1109/REAL.1992.242671}{DOI
  10.1109/REAL.1992.242671}, 1992, pp. 110--123.

\bibitem{DBLP:journals/tc/StrosniderLS95}
J.~K. Strosnider, J.~P. Lehoczky, and L.~Sha, ``The deferrable server algorithm
  for enhanced aperiodic responsiveness in hard real-time environments,''
  \emph{{IEEE} Trans. Comput.}, vol.~44,
  \href{http://dx.doi.org/10.1109/12.368008}{DOI 10.1109/12.368008}, no.~1, pp.
  73--91, 1995.

\bibitem{DBLP:journals/pe/LeungW82}
J.~Y. Leung and J.~Whitehead, ``On the complexity of fixed-priority scheduling
  of periodic, real-time tasks,'' \emph{Perform. Eval.}, vol.~2,
  \href{http://dx.doi.org/10.1016/0166-5316(82)90024-4}{DOI
  10.1016/0166-5316(82)90024-4}, no.~4, pp. 237--250, 1982.

\bibitem{audsley1993deadline}
N.~Audsley, A.~Burns, and A.~Wellings, ``Deadline monotonic scheduling theory
  and application,'' \emph{Control Engineering Practice}, vol.~1, no.~1, pp.
  71--78, 1993.

\bibitem{DBLP:journals/tc/ShaRL90}
L.~Sha, R.~Rajkumar, and J.~P. Lehoczky, ``Priority inheritance protocols: An
  approach to real-time synchronization,'' \emph{{IEEE} Trans. Comput.},
  vol.~39, \href{http://dx.doi.org/10.1109/12.57058}{DOI 10.1109/12.57058},
  no.~9, pp. 1175--1185, 1990.

\bibitem{dhall1978real}
S.~K. Dhall and C.~Liu, ``On a real-time scheduling problem,'' \emph{Operations
  Research}, vol.~26, no.~1, pp. 127--140, 1978.

\bibitem{DBLP:journals/rts/LopezGDG03}
J.~M. L{\'{o}}pez, M.~Garc{\'{\i}}a, J.~L. D{\'{\i}}az, and D.~F.
  Garc{\'{\i}}a, ``Utilization bounds for multiprocessor rate-monotonic
  scheduling,'' \emph{Real-Time Systems}, vol.~24,
  \href{http://dx.doi.org/10.1023/A:1021749005009}{DOI
  10.1023/A:1021749005009}, no.~1, pp. 5--28, 2003.

\bibitem{DBLP:journals/tpds/LopezDG04}
J.~M. L{\'{o}}pez, J.~L. D{\'{\i}}az, and D.~F. Garc{\'{\i}}a, ``Minimum and
  maximum utilization bounds for multiprocessor rate monotonic scheduling,''
  \emph{{IEEE} Trans. Parallel Distrib. Syst.}, vol.~15,
  \href{http://dx.doi.org/10.1109/TPDS.2004.25}{DOI 10.1109/TPDS.2004.25},
  no.~7, pp. 642--653, 2004.

\bibitem{DBLP:journals/tc/BaruahG03}
S.~K. Baruah and J.~Goossens, ``Rate-monotonic scheduling on uniform
  multiprocessors,'' \emph{{IEEE} Trans. Comput.}, vol.~52,
  \href{http://dx.doi.org/10.1109/TC.2003.1214344}{DOI
  10.1109/TC.2003.1214344}, no.~7, pp. 966--970, 2003.

\bibitem{DBLP:journals/rts/OhS94}
Y.~Oh and S.~H. Son, ``Enhancing fault-tolerance in rate-monotonic
  scheduling,'' \emph{Real-Time Systems}, vol.~7,
  \href{http://dx.doi.org/10.1007/BF01088524}{DOI 10.1007/BF01088524}, no.~3,
  pp. 315--329, 1994.

\bibitem{DBLP:journals/rts/GhoshMMS98}
S.~Ghosh, R.~G. Melhem, D.~Moss{\'{e}}, and J.~S. Sarma, ``Fault-tolerant
  rate-monotonic scheduling,'' \emph{Real-Time Systems}, vol.~15,
  \href{http://dx.doi.org/10.1023/A:1008046012844}{DOI
  10.1023/A:1008046012844}, no.~2, pp. 149--181, 1998.

\bibitem{DBLP:journals/tpds/BertossiMR99}
A.~A. Bertossi, L.~V. Mancini, and F.~Rossini, ``Fault-tolerant rate-monotonic
  first-fit scheduling in hard-real-time systems,'' \emph{{IEEE} Trans.
  Parallel Distrib. Syst.}, vol.~10,
  \href{http://dx.doi.org/10.1109/71.798317}{DOI 10.1109/71.798317}, no.~9, pp.
  934--945, 1999.

\bibitem{DBLP:conf/rtss/LehoczkySD89}
J.~P. Lehoczky, L.~Sha, and Y.~Ding, ``The rate monotonic scheduling algorithm:
  Exact characterization and average case behavior,'' in \emph{Proceedings of
  the Real-Time Systems Symposium},
  \href{http://dx.doi.org/10.1109/REAL.1989.63567}{DOI
  10.1109/REAL.1989.63567}, 1989, pp. 166--171.

\bibitem{DBLP:conf/rtss/KuoM91}
T.~Kuo and A.~K. Mok, ``Load adjustment in adaptive real-time systems,'' in
  \emph{Proceedings of the Real-Time Systems Symposium},
  \href{http://dx.doi.org/10.1109/REAL.1991.160369}{DOI
  10.1109/REAL.1991.160369}, 1991, pp. 160--170.

\bibitem{DBLP:journals/tc/BiniBB03}
E.~Bini, G.~C. Buttazzo, and G.~M. Buttazzo, ``Rate monotonic analysis: The
  hyperbolic bound,'' \emph{{IEEE} Trans. Comput.}, vol.~52,
  \href{http://dx.doi.org/10.1109/TC.2003.1214341}{DOI
  10.1109/TC.2003.1214341}, no.~7, pp. 933--942, 2003.

\bibitem{gardner1999}
M.~K. Gardner, ``Probabilistic analysis and scheduling of critical soft
  real-time systems,'' Ph.D. dissertation, University of Illinois at
  Urbana-Champaign, 1999.

\bibitem{DBLP:journals/tie/JiangZLDSGS15}
Y.~Jiang, H.~Zhang, Z.~Li, Y.~Deng, X.~Song, M.~Gu, and J.~Sun, ``Design and
  optimization of multiclocked embedded systems using formal techniques,''
  \emph{{IEEE} Trans. Ind. Electron.}, vol.~62,
  \href{http://dx.doi.org/10.1109/TIE.2014.2316234}{DOI
  10.1109/TIE.2014.2316234}, no.~2, pp. 1270--1278, 2015.

\bibitem{DBLP:journals/iandc/MeseguerR13}
J.~Meseguer and G.~Rosu, ``The rewriting logic semantics project: A progress
  report,'' \emph{Inf. Comput.}, vol. 231,
  \href{http://dx.doi.org/10.1016/j.ic.2013.08.004}{DOI
  10.1016/j.ic.2013.08.004}, pp. 38--69, 2013.

\bibitem{DBLP:journals/cacm/Leroy09}
X.~Leroy, ``Formal verification of a realistic compiler,'' \emph{Commun.
  {ACM}}, vol.~52, \href{http://dx.doi.org/10.1145/1538788.1538814}{DOI
  10.1145/1538788.1538814}, no.~7, pp. 107--115, 2009.

\bibitem{DBLP:conf/sosp/KleinEHACDEEKNSTW09}
G.~Klein, K.~Elphinstone, G.~Heiser, J.~Andronick, D.~Cock, P.~Derrin,
  D.~Elkaduwe, K.~Engelhardt, R.~Kolanski, M.~Norrish, T.~Sewell, H.~Tuch, and
  S.~Winwood, ``sel4: formal verification of an {OS} kernel,'' in
  \emph{Proceedings of the 22nd {ACM} Symposium on Operating Systems Principles
  2009}, \href{http://dx.doi.org/10.1145/1629575.1629596}{DOI
  10.1145/1629575.1629596}, 2009, pp. 207--220.

\bibitem{TianD2011}
C.~Tian and Z.~Duan, ``Model checking rate monotonic scheduling algorithm based
  on propositional projection temporal logic,'' \emph{Journal of Software},
  vol.~22, no.~2, pp. 211--221, 2011, in {Chinese}.

\bibitem{DBLP:conf/iceccs/CuiDT14}
J.~Cui, Z.~Duan, and C.~Tian, ``Model checking rate-monotonic scheduler with
  {TMSVL},'' in \emph{19th International Conference on Engineering of Complex
  Computer Systems}, \href{http://dx.doi.org/10.1109/ICECCS.2014.37}{DOI
  10.1109/ICECCS.2014.37}, 2014, pp. 202--205.

\bibitem{DBLP:journals/lisp/OlveczkyM07}
P.~C. {\"{O}}lveczky and J.~Meseguer, ``Semantics and pragmatics of {Real-Time
  Maude},'' \emph{Higher-Order and Symbolic Computation}, vol.~20,
  \href{http://dx.doi.org/10.1007/s10990-007-9001-5}{DOI
  10.1007/s10990-007-9001-5}, no. 1-2, pp. 161--196, 2007.

\bibitem{DBLP:journals/tcs/ClavelDELMMQ02}
M.~Clavel, F.~Dur{\'{a}}n, S.~Eker, P.~Lincoln, N.~Mart{\'{\i}}{-}Oliet,
  J.~Meseguer, and J.~F. Quesada, ``Maude: specification and programming in
  rewriting logic,'' \emph{Theor. Comput. Sci.}, vol. 285,
  \href{http://dx.doi.org/10.1016/S0304-3975(01)00359-0}{DOI
  10.1016/S0304-3975(01)00359-0}, no.~2, pp. 187--243, 2002.

\bibitem{DBLP:journals/jlp/Meseguer12}
J.~Meseguer, ``Twenty years of rewriting logic,'' \emph{J. Log. Algebr.
  Program.}, vol.~81, \href{http://dx.doi.org/10.1016/j.jlap.2012.06.003}{DOI
  10.1016/j.jlap.2012.06.003}, no. 7-8, pp. 721--781, 2012.

\bibitem{DBLP:journals/entcs/OlveczkyM07a}
P.~C. {\"{O}}lveczky and J.~Meseguer, ``Abstraction and completeness for
  {Real-Time Maude},'' \emph{Electr. Notes Theor. Comput. Sci.}, vol. 176,
  \href{http://dx.doi.org/10.1016/j.entcs.2007.06.005}{DOI
  10.1016/j.entcs.2007.06.005}, no.~4, pp. 5--27, 2007.

\bibitem{DBLP:journals/tse/KatcherAS93}
D.~I. Katcher, H.~Arakawa, and J.~K. Strosnider, ``Engineering and analysis of
  fixed priority schedulers,'' \emph{{IEEE} Trans. Softw. Eng.}, vol.~19,
  \href{http://dx.doi.org/10.1109/32.241774}{DOI 10.1109/32.241774}, no.~9, pp.
  920--934, 1993.

\bibitem{DBLP:journals/tse/Holzmann97}
G.~J. Holzmann, ``The model checker {SPIN},'' \emph{{IEEE} Trans. Softw. Eng.},
  vol.~23, \href{http://dx.doi.org/10.1109/32.588521}{DOI 10.1109/32.588521},
  no.~5, pp. 279--295, 1997.

\bibitem{DBLP:conf/icfem/HanDW12}
M.~Han, Z.~Duan, and X.~Wang, ``Time constraints with temporal logic
  programming,'' in \emph{Formal Methods and Software Engineering - 14th
  International Conference on Formal Engineering Methods, {ICFEM} 2012.
  Proceedings}, ser. Lecture Notes in Computer Science, vol. 7635,
  \href{http://dx.doi.org/10.1007/978-3-642-34281-3\_20}{DOI
  10.1007/978-3-642-34281-3\_20}, 2012, pp. 266--282.

\end{thebibliography}\
